\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-10-21 paper.Rmd
Removed shorts::

$W$ in equation \@ref(eq:velocity-time) represents Lambert's W function [@R-LambertW]. MSS and TAU parameters are estimated using `shorts::model_using_splits` function:

@@

m1 <- shorts::model_using_splits(
  distance = split_distance,
  time = split_time
)

@@

Once we have estimated MSS and TAU, we can use `shorts::predict_` family of functions to predict various relationships (i.e. time at distance, acceleration at distance, velocity at time):

```{r}
# Predict time at distance
shorts::predict_time_at_distance(
  distance = split_distance,
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU
)

# Predict acceleration at time
shorts::predict_acceleration_at_time(
  time = c(0, 1, 2, 3, 4, 5, 6),
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU
)
```

@@

df <- data.frame(
  distance = split_distance,
  time = split_time,
  pred_time = shorts::predict_time_at_distance(
    distance = split_distance,
    MSS = m1$parameters$MSS,
    TAU = m1$parameters$TAU
  )
)

@@

To estimate force production at distance or time (using `shorts::predict_force_at_distance` and `shorts::predict_force_at_time` functions), as well as power production (using `shorts::predict_power_at_distance` and `shorts::predict_power_at_time` functions), one needs to take into account the air resistance. Air resistance (N) is estimated using `shorts::get_air_resistance` function, which takes velocity, body mass (kg), body height (m), barometric pressure (Torr), air temperature ($C^\circ$), and wind velocity ($ms^-1$) as parameters (please refer to @arsacModelingEnergetics100m2002, @samozinoSimpleMethodMeasuring2016, and @vaningenschenauCanCyclePower1991 for more information):

```{r}
shorts::get_air_resistance(
  velocity = 5,
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)
```

When estimating force and power, the air resistance parameters can be set using `"..."`, which are forwarded to the `shorts::get_air_resistance`:

```{r}
# To calculate horizontal force produced
shorts::predict_force_at_distance(
  distance = split_distance,
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to shorts::get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)

# To calculate power produced
shorts::predict_power_at_distance(
  distance = split_distance,
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to shorts::get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)
```

The easiest way to get all kinematics for short sprints is to use `shorts::predict_kinematics` functions:

```{r}
df <- shorts::predict_kinematics(
  m1,
  max_time = 6,
  frequency = 100,
  # Additional parameters forwarded to shorts::get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)

@@

Another valuable addition for sport scientists and coaches is the ability to determine the distances and times where 90% of maximum sprinting speed is reached, or where peak power is within 90% range. To identify these values, \pkg{shorts} package comes with `shorts::find_` family of functions:

```{r}
# Finds distance where 90% of maximum sprinting speed is reached
shorts::find_velocity_critical_distance(
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  percent = 0.9
)

# Finds maximal power and distance (this time using air resistance)
shorts::find_max_power_distance(
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to shorts::get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)

# Finds distance over 90% power range
shorts::find_power_critical_distance(
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to shorts::get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)
```

@@

Sprint performance is often evaluated with a group of athletes (e.g., soccer club) representing a single strata of interest. Sports scientists can estimate individual profiles, or utilize mixed-effects models. To perform mixed-effects models in \pkg{shorts} for split times, one can use `shorts::mixed_model_using_splits` function. To demonstrate this functionality, we load the `split_times` dataset provided in the \pkg{shorts} package:

@@

# Mixed model
m2 <- shorts::mixed_model_using_splits(
  data = split_times,
  distance = "distance",
  time = "time",
  athlete = "athlete",

@@

m3 <- shorts::model_using_radar(
  velocity = sprint_velocity,
  time = sprint_time
)

@@

```{r}
m3_weighted <- shorts::model_using_radar(
  velocity = sprint_velocity,
  time = sprint_time,
  weights = 1 / (sprint_velocity + 1)
)

@@

Mixed-effects model using radar data is done using `shorts::mixed_model_using_radar` function. To perform mixed model, let's load data that comes with \pkg{shorts} package.

@@

m4 <- shorts::mixed_model_using_radar(
  radar_gun_data,
  time = "time",
  velocity = "velocity",
  athlete = "athlete"
)

@@

```{r}
# Without synchronization issues
m5 <- shorts::model_using_radar(
  velocity = df$velocity,
  time = df$`true time`
)

# With time added
m6 <- shorts::model_using_radar(
  velocity = df$velocity,
  time = df$`0.5s added`
)

# With time deducted
m7 <- shorts::model_using_radar(
  velocity = df$velocity,
  time = df$`0.5s deducted`
)

@@

This model is incorporated in the `shorts::model_using_radar_with_time_correction` function:

```{r}
# With time added
m8 <- shorts::model_using_radar_with_time_correction(
  velocity = df$velocity,
  time = df$`0.5s added`
)
coef(m8)

# With time deducted
m9 <- shorts::model_using_radar_with_time_correction(
  velocity = df$velocity,
  time = df$`0.5s deducted`
)
coef(m9)
```

When using `shorts::predict_` family of functions, one can provide estimated time correction to get predictions at original time scale.

@@

When it comes to mixed-model approach, time correction can be modeled as a fixed effect or random effect using the `shorts::mixed_model_using_radar_with_time_correction` function.

@@

# Mixed model with time correction being fixed effect
m10 <- shorts::mixed_model_using_radar_with_time_correction(
  radar_gun_data,
  time = "time",
  velocity = "velocity",
  athlete = "athlete",
  random = MSS + TAU ~ 1
)

@@

# Mixed model with time correction being random effect
m11 <- shorts::mixed_model_using_radar_with_time_correction(
  radar_gun_data,
  time = "time",
  velocity = "velocity",
  athlete = "athlete",
  random = MSS + TAU + time_correction ~ 1
)

@@

split_times <- tibble(
  distance = c(5, 10, 20, 30, 40),
  john_time = shorts::predict_time_at_distance(distance, MSS, TAU),

  # Jack's performance
  jack_distance = distance + 0.5,
  jack_true_time = shorts::predict_time_at_distance(jack_distance, MSS, TAU),
  time_05m = shorts::predict_time_at_distance(0.5, MSS, TAU),
  jack_time = jack_true_time - time_05m
)

@@

john_profile <- shorts::model_using_splits(
  distance = split_times$distance,
  time = split_times$john_time
)

jack_profile <- shorts::model_using_splits(
  distance = split_times$distance,
  time = split_times$jack_time
)

@@

sim_df <- sim_df %>%
  mutate(
    TAU = MSS / MAC,
    PMAX = MSS * MAC / 4,
    true_distance = distance + flying_start_distance,
    true_time = shorts::predict_time_at_distance(true_distance, MSS, TAU),
    stolen_time = shorts::predict_time_at_distance(flying_start_distance, MSS, TAU),
    time = true_time - stolen_time
  )

@@

```{r}
# Prediction wrapper
pred_wrapper <- function(data) {
  model <- shorts::model_using_splits(
    distance = data$distance,
    time = data$time
  )

@@

  predicted_time <- shorts::predict_time_at_distance(
    distance = data$distance,
    MSS = model$parameters$MSS,
    TAU = model$parameters$TAU
  )

@@

Rather than providing *apriori* time correction from the literature, \pkg{shorts} package provides an estimation of this parameter from the data provided, together with MSS and TAU. To estimate time correction, we use `shorts::model_using_splits_with_time_correction` function. Here is how we can estimate Jack parameters using either provided time correction (e.g., +0.3 and +0.5s) or estimated time correction:

```{r}
jack_profile_fixed_time_short <- shorts::model_using_splits(
  distance = split_times$distance,
  time = split_times$jack_time,
  time_correction = 0.3
)

jack_profile_fixed_time_long <- shorts::model_using_splits(
  distance = split_times$distance,
  time = split_times$jack_time,
  time_correction = 0.5
)

jack_profile_time_estimated <- shorts::model_using_splits_with_time_correction(
  distance = split_times$distance,
  time = split_times$jack_time
)

@@

This model is implemented in `shorts::model_using_splits_with_corrections` function. Below are the model estimates:

```{r}
jack_profile_distance_correction <- shorts::model_using_splits_with_corrections(
  distance = split_times$distance,
  time = split_times$jack_time
)

@@

```{r}
pred_wrapper <- function(data) {
  no_correction <- shorts::model_using_splits(
    distance = data$distance,
    time = data$time
  )

  fixed_correction_short <- shorts::model_using_splits(
    distance = data$distance,
    time = data$time,
    time_correction = 0.3
  )

  fixed_correction_long <- shorts::model_using_splits(
    distance = data$distance,
    time = data$time,
    time_correction = 0.5
  )

  time_correction <- shorts::model_using_splits_with_time_correction(
    distance = data$distance,
    time = data$time,
    control = nls.control(tol = 1)
  )

  time_dist_correction <- shorts::model_using_splits_with_corrections(
    distance = data$distance,
    time = data$time,
    control = nls.control(tol = 1)
  )

@@

  df$predicted_time <- shorts::predict_time_at_distance(
    distance = df$distance,
    MSS = df$est_MSS,
    TAU = df$est_TAU,
    time_correction = df$est_time_correction,
    distance_correction = df$est_distance_correction
  )

@@

Time correction and time and distance corrections are also implemented in the mixed-models using `shorts::mixed_model_using_splits_with_time_correction` and `shorts::mixed_model_using_splits_with_corrections`. We will showcase their use at the end of this article.

@@

sim_df <- sim_df %>%
  mutate(
    TAU = MSS / MAC,
    PMAX = MSS * MAC / 4,
    true_time = shorts::predict_time_at_distance(distance, MSS, TAU),
    time = true_time + time_lag
  )

@@

```{r}
jack_LOOCV <- shorts::model_using_splits_with_time_correction(
  distance = split_times$distance,
  time = split_times$jack_time,
  LOOCV = TRUE
)

@@

# No corrections model
bolt_m1 <- shorts::model_using_splits(
  distance = bolt_distance,
  time = bolt_time
)

# Model with reaction time as fixed time correction
bolt_m2 <- shorts::model_using_splits(
  distance = bolt_distance,
  time = bolt_time,
  time_correction = -bolt_reaction_time
)

# Model with estimated time correction
bolt_m3 <- shorts::model_using_splits_with_time_correction(
  distance = bolt_distance,
  time = bolt_time
)

# Model with estimated time correction, but deducted reaction time
bolt_m4 <- shorts::model_using_splits_with_time_correction(
  distance = bolt_distance,
  time = bolt_time - bolt_reaction_time
)

# Model with estimated time and distance corrections
bolt_m5 <- shorts::model_using_splits_with_corrections(
  distance = bolt_distance,
  time = bolt_time
)

# Model with estimated time and distance corrections and deducted reaction time
bolt_m6 <- shorts::model_using_splits_with_corrections(
  distance = bolt_distance,
  time = bolt_time - bolt_reaction_time
)

@@

```{r}
no_corrections <- shorts::mixed_model_using_splits(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete"
)

fixed_correction <- shorts::mixed_model_using_splits(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  time_correction = 0.3
)

time_correction_fixed <- shorts::mixed_model_using_splits_with_time_correction(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU ~ 1
)

time_correction_random <- shorts::mixed_model_using_splits_with_time_correction(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU + time_correction ~ 1
)

time_distance_correction_fixed <- shorts::mixed_model_using_splits_with_corrections(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU + time_correction ~ 1
)

time_distance_correction_random <- shorts::mixed_model_using_splits_with_corrections(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU + time_correction + distance_correction ~ 1
)
```

>>>>

$W$ in equation \@ref(eq:velocity-time) represents Lambert's W function [@R-LambertW]. MSS and TAU parameters are estimated using `model_using_splits` function:

@@

m1 <- model_using_splits(
  distance = split_distance,
  time = split_time
)

@@

Once we have estimated MSS and TAU, we can use `predict_` family of functions to predict various relationships (i.e. time at distance, acceleration at distance, velocity at time):

```{r}
# Predict time at distance
predict_time_at_distance(
  distance = split_distance,
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU
)

# Predict acceleration at time
predict_acceleration_at_time(
  time = c(0, 1, 2, 3, 4, 5, 6),
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU
)
```

@@

df <- data.frame(
  distance = split_distance,
  time = split_time,
  pred_time = predict_time_at_distance(
    distance = split_distance,
    MSS = m1$parameters$MSS,
    TAU = m1$parameters$TAU
  )
)

@@

To estimate force production at distance or time (using `predict_force_at_distance` and `predict_force_at_time` functions), as well as power production (using `predict_power_at_distance` and `predict_power_at_time` functions), one needs to take into account the air resistance. Air resistance (N) is estimated using `get_air_resistance` function, which takes velocity, body mass (kg), body height (m), barometric pressure (Torr), air temperature ($C^\circ$), and wind velocity ($ms^-1$) as parameters (please refer to @arsacModelingEnergetics100m2002, @samozinoSimpleMethodMeasuring2016, and @vaningenschenauCanCyclePower1991 for more information):

```{r}
get_air_resistance(
  velocity = 5,
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)
```

When estimating force and power, the air resistance parameters can be set using `"..."`, which are forwarded to the `get_air_resistance`:

```{r}
# To calculate horizontal force produced
predict_force_at_distance(
  distance = split_distance,
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)

# To calculate power produced
predict_power_at_distance(
  distance = split_distance,
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)
```

The easiest way to get all kinematics for short sprints is to use `predict_kinematics` functions:

```{r}
df <- predict_kinematics(
  m1,
  max_time = 6,
  frequency = 100,
  # Additional parameters forwarded to get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)

@@

Another valuable addition for sport scientists and coaches is the ability to determine the distances and times where 90% of maximum sprinting speed is reached, or where peak power is within 90% range. To identify these values, \pkg{shorts} package comes with `find_` family of functions:

```{r}
# Finds distance where 90% of maximum sprinting speed is reached
find_velocity_critical_distance(
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  percent = 0.9
)

# Finds maximal power and distance (this time using air resistance)
find_max_power_distance(
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)

# Finds distance over 90% power range
find_power_critical_distance(
  MSS = m1$parameters$MSS,
  TAU = m1$parameters$TAU,
  # Additional parameters forwarded to get_air_resistance
  # Otherwise, defaults are used
  bodymass = 80,
  bodyheight = 1.85,
  barometric_pressure = 780,
  air_temperature = 20,
  wind_velocity = 0.5
)
```

@@

Sprint performance is often evaluated with a group of athletes (e.g., soccer club) representing a single strata of interest. Sports scientists can estimate individual profiles, or utilize mixed-effects models. To perform mixed-effects models in \pkg{shorts} for split times, one can use `mixed_model_using_splits` function. To demonstrate this functionality, we load the `split_times` dataset provided in the \pkg{shorts} package:

@@

# Mixed model
m2 <- mixed_model_using_splits(
  data = split_times,
  distance = "distance",
  time = "time",
  athlete = "athlete",

@@

m3 <- model_using_radar(
  velocity = sprint_velocity,
  time = sprint_time
)

@@

```{r}
m3_weighted <- model_using_radar(
  velocity = sprint_velocity,
  time = sprint_time,
  weights = 1 / (sprint_velocity + 1)
)

@@

Mixed-effects model using radar data is done using `mixed_model_using_radar` function. To perform mixed model, let's load data that comes with \pkg{shorts} package.

@@

m4 <- mixed_model_using_radar(
  radar_gun_data,
  time = "time",
  velocity = "velocity",
  athlete = "athlete"
)

@@

```{r}
# Without synchronization issues
m5 <- model_using_radar(
  velocity = df$velocity,
  time = df$`true time`
)

# With time added
m6 <- model_using_radar(
  velocity = df$velocity,
  time = df$`0.5s added`
)

# With time deducted
m7 <- model_using_radar(
  velocity = df$velocity,
  time = df$`0.5s deducted`
)

@@

This model is incorporated in the `model_using_radar_with_time_correction` function:

```{r}
# With time added
m8 <- model_using_radar_with_time_correction(
  velocity = df$velocity,
  time = df$`0.5s added`
)
coef(m8)

# With time deducted
m9 <- model_using_radar_with_time_correction(
  velocity = df$velocity,
  time = df$`0.5s deducted`
)
coef(m9)
```

When using `predict_` family of functions, one can provide estimated time correction to get predictions at original time scale.

@@

When it comes to mixed-model approach, time correction can be modeled as a fixed effect or random effect using the `mixed_model_using_radar_with_time_correction` function.

@@

# Mixed model with time correction being fixed effect
m10 <- mixed_model_using_radar_with_time_correction(
  radar_gun_data,
  time = "time",
  velocity = "velocity",
  athlete = "athlete",
  random = MSS + TAU ~ 1
)

@@

# Mixed model with time correction being random effect
m11 <- mixed_model_using_radar_with_time_correction(
  radar_gun_data,
  time = "time",
  velocity = "velocity",
  athlete = "athlete",
  random = MSS + TAU + time_correction ~ 1
)

@@

split_times <- tibble(
  distance = c(5, 10, 20, 30, 40),
  john_time = predict_time_at_distance(distance, MSS, TAU),

  # Jack's performance
  jack_distance = distance + 0.5,
  jack_true_time = predict_time_at_distance(jack_distance, MSS, TAU),
  time_05m = predict_time_at_distance(0.5, MSS, TAU),
  jack_time = jack_true_time - time_05m
)

@@

john_profile <- model_using_splits(
  distance = split_times$distance,
  time = split_times$john_time
)

jack_profile <- model_using_splits(
  distance = split_times$distance,
  time = split_times$jack_time
)

@@

sim_df <- sim_df %>%
  mutate(
    TAU = MSS / MAC,
    PMAX = MSS * MAC / 4,
    true_distance = distance + flying_start_distance,
    true_time = predict_time_at_distance(true_distance, MSS, TAU),
    stolen_time = predict_time_at_distance(flying_start_distance, MSS, TAU),
    time = true_time - stolen_time
  )

@@

```{r}
# Prediction wrapper
pred_wrapper <- function(data) {
  model <- model_using_splits(
    distance = data$distance,
    time = data$time
  )

@@

  predicted_time <- predict_time_at_distance(
    distance = data$distance,
    MSS = model$parameters$MSS,
    TAU = model$parameters$TAU
  )

@@

Rather than providing *apriori* time correction from the literature, \pkg{shorts} package provides an estimation of this parameter from the data provided, together with MSS and TAU. To estimate time correction, we use `model_using_splits_with_time_correction` function. Here is how we can estimate Jack parameters using either provided time correction (e.g., +0.3 and +0.5s) or estimated time correction:

```{r}
jack_profile_fixed_time_short <- model_using_splits(
  distance = split_times$distance,
  time = split_times$jack_time,
  time_correction = 0.3
)

jack_profile_fixed_time_long <- model_using_splits(
  distance = split_times$distance,
  time = split_times$jack_time,
  time_correction = 0.5
)

jack_profile_time_estimated <- model_using_splits_with_time_correction(
  distance = split_times$distance,
  time = split_times$jack_time
)

@@

This model is implemented in `model_using_splits_with_corrections` function. Below are the model estimates:

```{r}
jack_profile_distance_correction <- model_using_splits_with_corrections(
  distance = split_times$distance,
  time = split_times$jack_time
)

@@

```{r}
pred_wrapper <- function(data) {
  no_correction <- model_using_splits(
    distance = data$distance,
    time = data$time
  )

  fixed_correction_short <- model_using_splits(
    distance = data$distance,
    time = data$time,
    time_correction = 0.3
  )

  fixed_correction_long <- model_using_splits(
    distance = data$distance,
    time = data$time,
    time_correction = 0.5
  )

  time_correction <- model_using_splits_with_time_correction(
    distance = data$distance,
    time = data$time,
    control = nls.control(tol = 1)
  )

  time_dist_correction <- model_using_splits_with_corrections(
    distance = data$distance,
    time = data$time,
    control = nls.control(tol = 1)
  )

@@

  df$predicted_time <- predict_time_at_distance(
    distance = df$distance,
    MSS = df$est_MSS,
    TAU = df$est_TAU,
    time_correction = df$est_time_correction,
    distance_correction = df$est_distance_correction
  )

@@

Time correction and time and distance corrections are also implemented in the mixed-models using `mixed_model_using_splits_with_time_correction` and `mixed_model_using_splits_with_corrections`. We will showcase their use at the end of this article.

@@

sim_df <- sim_df %>%
  mutate(
    TAU = MSS / MAC,
    PMAX = MSS * MAC / 4,
    true_time = predict_time_at_distance(distance, MSS, TAU),
    time = true_time + time_lag
  )

@@

```{r}
jack_LOOCV <- model_using_splits_with_time_correction(
  distance = split_times$distance,
  time = split_times$jack_time,
  LOOCV = TRUE
)

@@

# No corrections model
bolt_m1 <- model_using_splits(
  distance = bolt_distance,
  time = bolt_time
)

# Model with reaction time as fixed time correction
bolt_m2 <- model_using_splits(
  distance = bolt_distance,
  time = bolt_time,
  time_correction = -bolt_reaction_time
)

# Model with estimated time correction
bolt_m3 <- model_using_splits_with_time_correction(
  distance = bolt_distance,
  time = bolt_time
)

# Model with estimated time correction, but deducted reaction time
bolt_m4 <- model_using_splits_with_time_correction(
  distance = bolt_distance,
  time = bolt_time - bolt_reaction_time
)

# Model with estimated time and distance corrections
bolt_m5 <- model_using_splits_with_corrections(
  distance = bolt_distance,
  time = bolt_time
)

# Model with estimated time and distance corrections and deducted reaction time
bolt_m6 <- model_using_splits_with_corrections(
  distance = bolt_distance,
  time = bolt_time - bolt_reaction_time
)

@@

```{r}
no_corrections <- mixed_model_using_splits(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete"
)

fixed_correction <- mixed_model_using_splits(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  time_correction = 0.3
)

time_correction_fixed <- mixed_model_using_splits_with_time_correction(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU ~ 1
)

time_correction_random <- mixed_model_using_splits_with_time_correction(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU + time_correction ~ 1
)

time_distance_correction_fixed <- mixed_model_using_splits_with_corrections(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU + time_correction ~ 1
)

time_distance_correction_random <- mixed_model_using_splits_with_corrections(
  df,
  distance = "distance",
  time = "time",
  athlete = "Athlete",
  random = MSS + TAU + time_correction + distance_correction ~ 1
)
```
